---
title: "Data Confusion"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## R Markdown

This is my first markdown, how exciting! I am going to be using the diamonds data for this document since that is one we have become quite familiar with.

Large amounts of data can make interpretation pretty confusing sometimes. Learning R has made it more interesting to analyse data, experimenting with the different results and findings that you can create. 

Below are the average prices of diamonds split up by cut, confusingly resulting in an Ideal cut averaging a lower price than a Fair cut:

```{r cut}
ggplot(data=diamonds,mapping=aes(x=cut,y=price))+
  geom_boxplot()
```

## Including Plots

I also included a plot of the carat sized compared to price. Here we get a pretty different answer, showing that as the carat size gets larger the price gets bigger. 

```{r carat, echo=FALSE}
ggplot(data=diamonds,mapping=aes(x=carat,y=price))+
  geom_point()
```

This took me a while to mess around with in order to get the tables and graphs right even though they are from different data sets!

We can see though that data has lots of variables with many ranges, so here we see that there can be many different sized diamonds for different prices and that even a small carat can be worth a lot of money. All data is important! I hope you enjoyed my first markdown! 
