---
title: "Diamond sizes"
date: 2016-08-25
output: html_document
---

```{r setup}
library(ggplot2)
library(dplyr)

smaller <- diamonds %>% 
  filter(carat <= 2.5)

comma <- function(x){
  format(x,digits=2,big.mark=",")
}

large <- nrow(diamonds)-nrow(smaller)
percent <- large/nrow(smaller)*100
```

We have data about `r comma(nrow(diamonds))` diamonds. Only 
`r large` (`r round(percent,1)`%) are larger than
2.5 carats. The distribution of the remainder is shown
below:

```{r, echo = FALSE}
smaller %>% 
  ggplot(aes(carat)) + 
  geom_freqpoly(binwidth = 0.01)
```

## Size by Cut, Color, and Clarity

Here we can see that diamonds with a lower quality cut (Fair) tend to be bigger than diamonds of a higher quality (Ideal). 

```{r diamond size}

ggplot(data=diamonds,mapping=aes(x=cut,y=carat))+
  geom_boxplot()
```

Here we can see below, when comparing color to carat, that as the color worsens (moving towards J) the diamonds become larger. 

```{r}
ggplot(diamonds,mapping=aes(x=color,y=carat))+
  geom_boxplot()
```

I do not know much about diamonds, but I can assume that the pattern as we've seen stays the same. As you can see below, when the clarity of the diamond worsens (moving towards I1) the diamonds get bigger. 

```{r}
ggplot(diamonds,mapping=aes(x=clarity,y=carat))+
  geom_boxplot()
```

## Largest 20 Diamonds

Below we have a table displaying the 20 largest diamonds with details about their most important attributes; cut, color, and clarity.

```{r largest}

diamonds%>%
  arrange(desc(carat))%>%
  slice(1:20)%>%
  select(carat,cut,color,clarity)
```
