
---
title: "Aaron's Markdown"
output: html_document
---


## R Markdown

This is my first markdown, how exciting! I am going to be using the NYC flight details for this document since that is one we have become quite familiar with.

Enjoy this random information about flights from New York City in the year of 2013. Learning R has made it more interesting to analyse data, experimenting with the different results and finding that you can create. 

Below are the flights sorted out so that you can see which were the most delayed:

```{r setup, include=FALSE}
library(ggplot2)
library(dplyr)

delay <- flights%>%
  filter(dep_delay<=120,arr_delay<=120)
```

## Including Plots

I also included a plot of the cars data we became familiar with. Below is the relationship between the engine size (displ) and fuel efficiency (hwy) separated by class in color:

```{r cars, echo=FALSE}
delay%>%
  ggplot(aes(dep_delay))+
  geom_freqpoly()
```

This took me a while to mess around with in order to get the tables and graphs right even though they are from different data sets! I hope you enjoyed my first markdown! 